Paper notes

### 2019-08-15 paper_notes.Rmd
Add files via upload

e_w <-
e_w_ng <- 
i_v <- 
M <- 
S <-

>>>>

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 1
M <- 0

fvf0p  <- f_val(e_w,0,M,i_v,S)
fvf1p  <- f_val(e_w,0.1,M,i_v,S)
fvf2p   <- f_val(e_w,0.2,M,i_v,S)
fvf3p   <- f_val(e_w,0.3,M,i_v,S)
fvf4p   <- f_val(e_w,0.4,M,i_v,S)
fvf5p   <- f_val(e_w,0.5,M,i_v,S)
fvf6p   <- f_val(e_w,0.6,M,i_v,S)
fvf7p   <- f_val(e_w,0.7,M,i_v,S)
fvf8p   <- f_val(e_w,0.8,M,i_v,S)
fvf9p  <- f_val(e_w,0.9,M,i_v,S)
fvf10p  <- f_val(e_w,1.0,M,i_v,S)

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 1

fvf0t <- f_val(e_w,0,M,i_v,S)
fvf1t  <- f_val(e_w,0.1,M,i_v,S)
fvf2t   <- f_val(e_w,0.2,M,i_v,S)
fvf3t   <- f_val(e_w,0.3,M,i_v,S)
fvf4t   <- f_val(e_w,0.4,M,i_v,S)
fvf5t   <- f_val(e_w,0.5,M,i_v,S)
fvf6t  <- f_val(e_w,0.6,M,i_v,S)
fvf7t   <- f_val(e_w,0.7,M,i_v,S)
fvf8t   <- f_val(e_w,0.8,M,i_v,S)
fvf9t  <- f_val(e_w,0.9,M,i_v,S)
fvf10t  <- f_val(e_w,1.0,M,i_v,S)

x_graph_val <- seq(0.0,1.0, by = 0.1) #rep(seq(0.0,1.0, by = 0.1),2)
uti_val_pf <- c(fvf0p,fvf1p,fvf2p,fvf3p,fvf4p,fvf5p,fvf6p,fvf7p,fvf8p,fvf9p,fvf10p)
uti_val_th <- c(fvf0t,fvf1t,fvf2t,fvf3t,fvf4t,fvf5t,fvf6t,fvf7t,fvf8t,fvf9t,fvf10t)

symm_val <- data.frame(x_graph_val,uti_val_pf)
threshold_val <- data.frame(x_graph_val,uti_val_th)

# funct_symm_v <- c(rep("symmetric",9),rep("threshold",9))

symm_val_graph <- ggplot(symm_val,aes(x_graph_val,uti_val_pf))
thres_val_graph <- ggplot(threshold_val,aes(x_graph_val,uti_val_th))

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

# symm_val_plot
# thres_val_plot

suppressWarnings(
grid.arrange(symm_val_plot, thres_val_plot, ncol= 2,nrow = 2)
)
